Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-16 docs/questioning.tex
adding some definitions

>>>>

\section{Intrusion Detection Accuracy}

An intrusion detection system examines some software artifact and
reports vulnerabilities. The value an intrusion detection system can
be measured in terms of its \emph{accuracy}, which gauges the quality
of its output. An intrusion detection system makes predictions for
vulnerabilities. The following may happen:
\begin{itemize}
\item A prediction about a vulnerability is true. That is a \emph{true
    positive}. 
\item A prediction about a vulnerability is false; intrusion
  detection reported something that in reality is not vulnerability.
  That is a \emph{false positive}.
\item A prediction about the absence of a vulnerability is true. That
  is a \emph{true negative}: intrusion detection evaluated something
  as being safe, and it is.
\item A prediction about the absence of a vulnerability is false. That
  is a \emph{false negative}: intrusion detection missed a
  vulnerability.
\end{itemize}
In terms of the above, the \emph{Positive Predictive Value} (PPV) is
defined as the ratio of true positives over all reported positives,
while the \emph{Negative Predictive Value} (NPV) is defined as the
ratio of true negatives over all reported negatives. In intrusion
detection, the PPV is an indicator of how much we should be worried
about a reported vulnerability being true. Conversely, the NPV is an
indicator of how much we should be reassured when no vulnerabilities
are reported.

What we need to proceed:
\begin{itemize}
\item Do the studies report the sample size? Note that we must be
  careful with what we mean by sample size. A single item in the
  sample is something that can be vulnerable or not. 
\item Do the studies report true positives, false positives, true
  negatives, false negatives?
\end{itemize}
